---
title: "Farsr package How-to"
author: "Vladimir Semitchev"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
knitr::opts_knit$set(root.dir = file.path(find.package("farsr"),"extdata"))
library(farsr)
library(maps)
```
farsr package can be used in mutiple ways

### First, to load the data from a CSV report file downloaded from FARS to a dataframe

```{r eval=FALSE}
df <- fars_read(system.file("extdata","accident_2014.csv.bz2",package="farsr"))
```

### Second, to load the FARS report data for multiple years


```{r eval=FALSE}
mon_year <- fars_read_years(c(2013,2014,2015))
```

### Third, to generate a summary report for each month of each year from the list of years.

```{r}
smry <- fars_summarize_years(c(2014,2015))
```

### Finally, it can generate a map of the give state showing location of each accident

```{r}
fars_map_state(6,2015)
```

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
